---
title: "Practical 10 Multiple Linear Regression"
author: "Jay Patel"
date: "10/23/2020"
output: html_document

runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Multipal linear Regression 

Multiple linear regression (MLR), also known simply as multiple regression, is a statistical technique that uses several explanatory variables to predict the outcome of a response variable. The goal of multiple linear regression (MLR) is to model the linear relationship between the explanatory (independent) variables and response (dependent) variable.

\(Y_i = \beta_0 + \beta_1 * X_1 + \beta_2 * X_2 + ... +  \beta_n * X_n\)

while 

\(Y_i\) is value of the response variable,

\(X_i\) is value of the propose variable,

\(\beta_0 , \beta_1,\beta_3,..,\beta_n\) are the parameters (Regression coefficients),


## choose a file 

```{r}
inputPanel({
  fileInput("file1","choose csv file",multiple=FALSE)
})
 data1 <- reactive(read.csv(input$file1$datapath))
 lc <- reactive(data1()$lc)
 mileage <- reactive(data1()$Mileage)
 lh <- reactive(data1()$lh)
```

## Data

Lc = [`r lc`]

Mileage = [`r mileage`]

Lh = [`r lh`]


## pairs Plot

```{r , echo=TRUE}
renderPlot(pairs(data1()[3:5]))
```


## Multipal Linear Model

```{r , echo=TRUE}

Model1 <- reactive(lm(lc ~ Mileage + lh ,data = data1()))
reactive(lm(lc ~ Mileage + lh ,data = data1()))
reactive(summary(lm(lc ~ Mileage + lh ,data = data1())))

```
