---
title: "Simple Linear Regression"
author: "Aniket Roy and Krutik Shah"
date: "10/23/2020"
output:
  html_document: default
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Simple linear Regression 

The Simple linear Regression model is used to propose (independent) variable based on predictor variable (dependent) .The linear Regression model can be be stated as follows 

\(Y_i = \beta_0 + \beta_1 * X_i + e_i\)

while 

\(Y_i\) is value of the response variable,

\(X_i\) is value of the propose variable,

\(\beta_0 , \beta_1\) are the parameters (Regression coefficients),

\(e_i\) radon error turn with \(E(e_i) = 0 and V(e_i) = \sigma^2\)

## choose a file 
```{r}
inputPanel({
  fileInput("file1","choose csv file",multiple=FALSE)
})
 data1 <- reactive(read.csv(input$file1$datapath))
 year <- reactive(data1()$Year)
 snowfall <- reactive(data1()$Snowfall)
```

## Data

Year = [`r year`]

Snowfall = [`r snowfall`]

## Correlation coffcitent 

```{r , echo=TRUE}
reactive(cor(year(),snowfall()))
```

from the above output we see that the correlation between year and snowfall is -0.8378. hence the positive linear relationship between year and snowfall is quite strong but they are negative correlation

## Scatter Plot

```{r , echo=TRUE}
renderPlot(plot(year(),snowfall()))
```

## Significance test 

```{r , echo=TRUE}
res <- reactive(cor.test(year(),snowfall()))
```

## Linear Model

```{r , echo=TRUE}
Model1 <- reactive(lm(snowfall()~year()))
reactive(Model1)
b = reactive(Model1()$coefficients[1])
a = reactive(Model1()$coefficients[2])
```

the filled model is: snowfall = `r a`*Year + `r b`